---
title: "Exercise #X"
subtitle: "Fortgeschrittene Statistische Software für NF"
author: "Valentin Haury (12686340)"
date: "`r Sys.Date()`"
output: distill::distill_article
---

## Librarys

```{r}
# in this codeblock the most important libraries are loaded
  library(ggplot2)
  library(dplyr)
  library(readr)
  library(tidyverse)
  library(knitr)
  library(easystats)
```


## Exercise 1: Initializing git (4 Points)

For this whole exercise sheet we will be tracking all our changes to it
in git.

a)  
b)  
c) 

d)

- strength:
  - backups of the project can be used to undo changes
  - version control that makes working on projects in teams easier and helps merging different versions of a project
- weaknesses:
  - extra effort needed to create and update the project in git
  - multiple different versions can exist at the same time, possibly creating confusion
  
e)


## Exercise 2: Putting your Repository on GitHub (3 Points)

For this task you will upload your solution to GitHub.

a)  Link to the repository:

[GitHub](https://github.com/valentinhaury/exeRcise-sheet-3)

b)  
c)


## Exercise 3: Pixar Films (4 Points)

a)

```{r}
#Load data 
pixar_films <- readr::read_csv('data/pixar_films.csv')
#remove movies without title
pixar_films <- pixar_films %>% filter(!is.na(film))
#inspect "film_rating"
pixar_films %>% distinct(film_rating) %>% head(10)
#create factor film_rating_factor
pixar_films$film_rating_factor <- factor(pixar_films$film_rating)

```

The variable "film_rating" can have the values:
 - G    :suitable for the general audience
 - PG   :parental guidance is suggested
 - N/A  :no rating available 
 
A factor variable consists of finite nominal or ordinal categories. The film_rating variable fits this restrictions.

b)
    
```{r}
#adding series variable to all movies
pixar_films <- pixar_films %>% 
  mutate(
    series = case_when(
      film %in% c("Toy Story", "Toy Story 2", "Toy Story 3", "Toy Story 4") ~ "Toy Story",
      film %in% c("Monsters, Inc.", "Monsters University") ~ "Monsters",
      film %in% c("The Incredibles", "Incredibles 2") ~ "Incredibles",
      film %in% c("Cars", "Cars 2", "Cars 3") ~ "Cars",
      film %in% c("Finding Nemo", "Finding Dory") ~ "Nemo",
      TRUE ~ film
    ) 
  ) %>%
  group_by(series) %>%
  mutate(count = n()) %>%
  ungroup()

#creating series dataframe with movie-titles as one String
pixar_series <- pixar_films %>%
  group_by(series) %>%
  summarise(
    movies_in_series = paste(film, collapse = ", "),
    film_count = n(),
    .groups = "drop"
  )
#output
pixar_series %>% head(10)
```
    
    
Toy Story: Toy Story; Toy Story 2; Toy Story 3; Toy Story 4
Monsters: Monsters, Inc.; Monsters University
Incredibles: The Incredibles; Incredibles 2
Cars: Cars; Cars 2; Cars 3
Nemo: Finding Nemo; Finding Dory

c)  

```{r}
#loading data
public_response <- readr::read_csv('data/public_response.csv')
#changing cinema_score to ascending factor
public_response$cinema_score <- factor(public_response$cinema_score,
                                             levels = c("A-", "A", "A+"),
                                             ordered = TRUE)
#combining the dataframes
pixar_films <- full_join(pixar_films, public_response, by = "film")
```

d)  

```{r}
#plot for Pixar-series with more then 1 movie
pixar_films %>% 
  filter(count > 1) %>%
  ggplot(aes(y = metacritic, x = series, fill = film, group = interaction(series, release_date))) +
    geom_bar(stat = "identity", position = position_dodge()) +
    labs(x="Series", y = "Metacritic-Score", title = "Metacritic-Score for Pixar-movies grouped by Series", fill = "Movie") +
    theme(axis.text.x = element_text(angle = 60, hjust = 1))
```

The first movie of a series always has the best Metacritic-Score. If there is a 3rd movie it is better then the 2nd one, but in general the movies of a series decline in quality acording to the Metacritic-Score.   


## Exercise 4: Open Analysis (4 points)

a)  
b)  
c)  

-   Dataset Name: Life satisfaction – Eurobarometer (2017)
-   Link: <https://github.com/owid/owid-datasets/tree/master/datasets/Life%20satisfaction%20%E2%80%93%20Eurobarometer%20(2017)>

d)  

Does winning the FIFA worldcup change the percieved Life Satisfaction of people in a european country compared to the rest of europe?
This question explores the psychological and emotional impact of national events on subjective well-being.

To answer this question the Eurobarometer data will be analyzed for the years listed below and the countries Italy, Germany, France and Spain.

1982 Italy
1990 Germany
1998 France
2006 Italy
2010 Spain
2014 Germany
2018 France

e) 
    
```{r}
#read the data and change the column names for easier access
eurobarometer <- read.csv("data/Life satisfaction – Eurobarometer (2017).csv") 
colnames(eurobarometer) <- c("Country", "Year", "Happiness")

#create a df with the winning nations/years
winners <- data.frame(
  Country = c("Italy", "Germany", "France", "Italy", "Spain", "Germany", "France"),
  Year = c(1982, 1990, 1998, 2006, 2010, 2014, 2018)
)


#add a variable to track if a nation won in a certain year
eurobarometer <- eurobarometer %>%
  mutate(WonWorldCup = if_else(
    paste(Country, Year) %in% paste(winners$Country, winners$Year),
    1, 0
  ))

#function that gets the difference in happiness to the year before in a given country
get_happiness_change <- function(df, country, year) {
  h_before <- df$Happiness[df$Country == country & df$Year == year - 1]
  h_win    <- df$Happiness[df$Country == country & df$Year == year]
  
  if (length(h_win) == 1 && length(h_before) == 1) {
    return(h_win - h_before)
  } else {
    return(NA)
  }
}

#computing the happiness change in the winning countries comparing it to the rest of europe
results <- winners %>%
  rowwise() %>%
  mutate(
    Change_Winner = get_happiness_change(eurobarometer, Country, Year),
    Change_Europe = get_happiness_change(eurobarometer, "European Union", Year),
    Diff = Change_Winner - Change_Europe
  ) %>%
  ungroup()

#computing the change in happiness compared to the rest of europe
average_change_compared_to_europe <- results %>%
  summarise(
    avg_chg = mean(Diff, na.rm = TRUE),
    sd_chg  = sd(Diff, na.rm = TRUE)
  )

#computing the absolute change in happiness
avg_change <- results %>%
  summarise(
    avg_chg = mean(Change_Winner, na.rm = TRUE),
    sd_chg  = sd(Change_Winner, na.rm = TRUE)
  )

```
 
On average the winnig nations perceived happiness is `r round(avg_change$avg_chg, 2)` with a standard deviation of `r round(avg_change$sd_chg, 2)` percent-points higher in the year of the worldcup compared to the year before the worldcup. But this increase is `r round(average_change_compared_to_europe$avg_chg, 2)` percent-points lower then the increase in the rest of Europe with a standard deviation of `r round(average_change_compared_to_europe$sd_chg, 2)` . Because of the high standard deviation the influence of winning a world cup on the happiness of a nation cant be determined with the used method and the Eurobarometer dataset. Other events like political decisions probably have bigger infuences that hide the influence of this particular sport event.
    
    
f) 

```{r plot-happiness, fig.cap="Happiness over time for World Cup winners and Europe. Markers indicate winning years."}
#filtering only the countrys that won a worldcup and adding the WonWorldCup variable to show the years where a worldcup was won
plot_data <- eurobarometer %>%
  mutate(WonWorldCup = paste(Country, Year) %in% paste(winners$Country, winners$Year)) %>%
  filter(Country %in% c(winners$Country, "European Union")) 

#drawing the line plot
ggplot(plot_data, aes(x = Year, y = Happiness, color = Country)) +
  geom_line(size = 1) +
  geom_point(data = subset(plot_data, WonWorldCup == TRUE),
             aes(x = Year, y = Happiness),
             shape = 21, fill = "gold", size = 3, stroke = 1.2) +
  theme_minimal() +
  labs(
    y = "Share of People Who Are Happy (%)",
    x = "Year",
    color = "Country"
  )

```

