---
title: "Exercise #X"
subtitle: "Fortgeschrittene Statistische Software für NF"
author: "Valentin Haury (12686340)"
date: "`r Sys.Date()`"
output: distill::distill_article
---

## Librarys

```{r}
# in this codeblock the most important libraries are loaded
  library(ggplot2)
  library(dplyr)
  library(readr)
  library(tidyverse)
  library(knitr)
  library(easystats)
```



## Exercise 1: Initializing git (4 Points)

For this whole exercise sheet we will be tracking all our changes to it
in git.

a)  
b)  
c) 

d)  
- strength:
  - backups of the project can be used to undo changes
  - version control that makes working on projects in teams easier and helps merging different versions of a project
- weaknesses:
  - extra effort needed to create and update the project in git
  - multiple different versions can exist at the same time, possibly creating confusion
  
e)

## Exercise 2: Putting your Repository on GitHub (3 Points)

For this task you will upload your solution to GitHub.

a)  Link to the repository:

[GitHub](https://github.com/valentinhaury/exeRcise-sheet-3)
b)  
c)

## Exercise 3: Pixar Films (4 Points)

Download the `pixar_films` and `public_response` datasets from the
GitHub repository and track them in git.

Link:
<https://github.com/rfordatascience/tidytuesday/tree/main/data/2025/2025-03-11>

For small datasets like these adding them to git is not a problem.

a)DOWNLOAD DATA AND ADD TO MY OWN GIT
    
```{r}
#Load data 
pixar_films <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/main/data/2025/2025-03-11/pixar_films.csv')
#remove movies without title
pixar_films <- pixar_films %>% filter(!is.na(film))
#inspect "film_rating"
pixar_films %>% distinct(film_rating) %>% head(10)
#create factor film_rating_factor
pixar_films$film_rating_factor <- factor(pixar_films$film_rating)

```

The variable "film_rating" can have the values:
 - G    :suitable for the general audience
 - PG   :parental guidance is suggested
 - N/A  :no rating available 
 
A factor variable consists of finite nominal or ordinal categories. The film_rating variable fits this restrictions.

b)  Inspect the film titles manually. Which films form a film series? A
    film series can be identified by a common word in the titles of the
    films, often in conjunction with a number in the title,
    e.g. "Despicable Me" and "Despicable Me 2". Create a dataframe which
    displays a list of the different series with the titles of the films
    and how many films belong to the series. Output the dataframe.

c)  Load the `public_response` dataframe into R. Convert the
    `cinema_score` variable into a factor while ensuring the factor
    levels are defined in ascending order, from the lowest to the
    highest score. Combine `public_response` with the `pixar_films`
    dataset using an appropriate merge variable.

d)  Choose one of the variables representing the public response and
    create a bar plot for the films belonging to a series. Here are the
    details of the plot:

    -   The film series are represented on the x-axis.
    -   Your chosen public response variable is displayed on the y-axis.
    -   Each film in the series is represented as a separate bar. Bars
        are grouped by film under their respective series on the x-axis.
        Order the bars within a series according to the release date of
        the films.
    -   A title and axis labels for context.

    What do you notice when comparing the scores of the films in a
    series? Do you see any patterns?

## Exercise 4: Open Analysis (4 points)

This exercise is a bit more open-ended. You can choose any dataset from
[Our World in Data](https://ourworldindata.org/) and analyze it, while
determining the research question yourself.

a)  Go to <https://github.com/owid/owid-datasets/tree/master/datasets>
    and choose a dataset that interests you. You can have a look at
    <https://ourworldindata.org/> to gather some inspiration.
b)  Download the dataset and track it in git.
c)  Put the name / title of the dataset and a link to it below.

-   Dataset Name: ...
-   Link: <https://github.com/owid/owid-datasets/>...

d)  Come up with a (research) question you want to answer with the data
    and briefly explain why you believe this is an interesting question
    within one sentence. It should be a question that can be answered
    with the dataset and using R.
e)  Use R to answer your chosen question. Please limit your analysis to
    the functions and techniques we have covered so far in the course.
    You are **not expected** to use advanced statistical models or
    external packages which haven't been introduced.
f)  Create a meaningful plot / figure with the dataset. Make sure to
    provide a figure caption (via the chunk options / Rmarkdown) and
    correctly label the figure.

## Final Note

Make sure to push all your commits and changes to GitHub before
submitting the exercise sheet.
